A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-04 paper.tex

\begin{abstract}
We give a complete classification of twists of supersymmetric Yang-Mills theories with in dimensions~$2\leq n \leq 10$.
We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
For each class of square-zero supercharges in the supersymmetry algebra, we give a description of the corresponding twisted theory in terms of partially holomorphic and topological versions of Chern-Simons and $BF$ theory. 
\end{abstract}

@@

To summarize, supersymmetric twisting consists of the following three steps:
\begin{enumerate}
\item Choose a square-zero supercharge $Q\in\Sigma$ and modify the differential of the theory as $\mathrm{d}\mapsto\mathrm{d}+Q$.

@@

>>>>

\begin{abstract}
We give a complete classification of twists of supersymmetric Yang-Mills theories in dimensions~$2\leq n \leq 10$.
We formulate supersymmetric Yang-Mills theory classically using the BV formalism, and then we construct an action by the supersymmetry algebra using the language of $L_\infty$ algebras.
For each class of square-zero supercharges in the supersymmetry algebra, we give a description of the corresponding twisted theory in terms of partially holomorphic and topological versions of Chern-Simons and $BF$ theory. 
\end{abstract}

@@

To summarize, supersymmetric twisting consists of the following three steps:

\begin{enumerate}
\item Choose a square-zero supercharge $Q\in\Sigma$ and modify the differential of the theory as $\mathrm{d}\mapsto\mathrm{d}+Q$.

@@

% \item  Context and literature on twists, including in the BV formalism.  There's a perspective there in terms of derived algebraic geometry (our mapping stacks we like to talk about).  Also at least a remark on the perspective in terms of coupling to twisted sugra.
% \item  perspective in terms of twisting homomorphisms, and putting twisted theories on curved backgrounds.
% \item  Mathematical literature on SUSY Yang-Mills, including Baez-Huerta and references therein.
% \item  Strategy for computations: coupling to background fields, homotopical SUSY action (reference Baulieu et al), proving the CME is satisfied including the background symmetry fields, then computing the twist in terms of the EOM in a few examples, and computing many other examples via dimensional reduction.
% \item  EOM of A-twists, and connection to various PDEs of interest in QFT.
% \item  Connection between twisted BV theories and twisted factorization algebras, and therefore to our earlier paper on $\bb E_n$ algebras.
% \item  Quantization: for cotangent theories and their deformations there's a 1-loop exact prequantization, just need to calculate the 1-loop anomaly to the QME.  In many cases this is worked out.
%\end{enumerate}}

\subsection*{Applications to quantization}
%\addcontentsline{toc}{subsection}{Applications to quantization}

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
This theory of renormalization can been used to study field theories with and without supersymmetry. \brian{many citations}
In the context of (non-supersymmetric) Yang-Mills theory, for instance, it is shown that this theory recovers asymptotic freedom by an explicit analysis of the local counterterms present in the four-dimensional gauge theory \cite{EWY}.

In principle, the existence of local counterterms can be used to analyze the full untwisted supersymmetric gauge theories in a mathematically rigorous way.
In practice, however, our approach to renormalization does not provide any significant advantage over traditional approaches used in QFT.

A significant simplification happens at the level of {\em twisted} supersymmetric Yang-Mills theories that we study in this work. 
For few examples, but not all, the twisted theory turns out to be a {\em topological field theory}. 
The theory of renormalization for topological theories can be handled using configuration spaces \cite{Kontsevich}. \brian{more examples}

There are drawbacks to the traditional approach to studying TFTs in the context of supersymmetric Yang-Mills theory.
For instance, upon performing a topological twist, when it exists, one can argue that a significant portion of the data of the full supersymmetric field theory is lost.
Furthermore, there are many examples of twists of supersymmetric field theories that are not topological, so the usual methods of TFT do not apply even at the twisted level. 
Perhaps the most fundamental example of this is $10$-dimensional supersymmetric Yang-Mills theory, where no topological twist exists.

We show that while not every twist results in a topological field theory, it does result in a theory in which some directions of spacetime behave topologically, and the remaining directions behave holomorphically. 
For a translation invariant field theory, this means that at least half of the linearly independent translation invariant vector fields act on the field theory in a BRST exact way, but it is possible that more than half of the translation invariant vector fields act trivially in cohomology.

Inspired by the work of Costello and Li in \cite{BCOV1} and Li in \cite{LiVertex, LiFeynman}, the foundations of renormalization for mixed holomorphic / topological field theories on Euclidean space has been developed in \cite{BWhol}.
The key result is that the renormalization for mixed holomorphic / topological theories is extremely well-behaved from an analytic perspective. 
It is shown in the cited work that to first order in $\hbar$, the renormalization of mixed holomorphic/topological theory is {\em finite}. 
Furthermore, in \cite{LiVertex}, it is shown that in real dimension two this holds to all orders in $\hbar$.

These results yield a salient approach to mathematically characterizing the one-loop quantization of every twist of supersymmetric Yang-Mills theory. 
Furthermore, in many examples of theories obtained via twisting not much is lost when asking for the one-loop quantization.
The twisted gauge theories of type $BF$, which are plentiful in the examples we consider,  admit quantizations which are exact at one loop; meaning all higher order corrections vanish identically. 
While ambitious, the first natural problem would be to compute anomalies which we plan to return to in future work.

\subsection*{The relationship to factorization algebras}
